---
title: "africa-data-exact"
date: "7/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data Management for "Public opinion effects of digital state repression: How Internet outages shape government evaluation in Africa"
24.01.2023

Required packages
```{r}
rm(list=ls())
library(stargazer)
library(tidyverse)
library(readxl)
library(haven) #load SPSS
library(hms) #convert characters to time variables
library(ggplot2)
library(vistime)
library(MASS)
library(lubridate)
library(countrycode)
library(gridExtra)
library(grid)

library(sf)
library(afriadmin)
library(sp)
library(raster)
library(tmap)

```


Load data 
```{r}
afro.data <- read_sav("r7_merged_data_34ctry.release.sav")
ioda.data <- read.csv("ioda_data.csv")
```


Modify merged data from Afrobarometer Round 7
```{r}
###select variables of interest
afro.data <- dplyr::select(afro.data, RESPNO, COUNTRY, REGION, DATEINTR, STRTIME, Q1, Q13, Q36, Q43A, Q43B, Q43D, Q43F, Q58A, Q58B, Q58C, Q97, Q101, Q104)
names(afro.data) <- c("respno", "country", "region", "day", "time", "age", "pol_intr", "democr", "trst_pres", "trst_parl", "trst_local", "trst_opposition", "perf_pres", "perf_parl", "perf_local", "edu", "female", "housing")
head(afro.data)

###assign value label to Afrobarometer (original file is in SPSS)
afro.data$country
c <- stack(attr(afro.data$country, 'labels')) #labels of country names
names(c) <- c("country", "country_name" )
afro.data <- left_join(afro.data, c, by="country")

afro.data$region
x <- stack(attr(afro.data$region, 'labels')) #labels of region names
names(x) <- c("region", "region_name" )
afro.data <- left_join(afro.data, x, by="region")

rm(c,x)

###assign start date and time of interviews
afro.data$interview <- as.POSIXct(paste(afro.data$day, afro.data$time), format="%Y-%m-%d %H:%M:%S")



```

```{r}
###Survey overview per country
dates <- afro.data %>%
   group_by(country_name) %>%
   summarise(startintv = min(day), endintv = max(day)) 

###add start and endday of survey in the individual country to dataframe
afro.data <- left_join(afro.data, dates, by="country_name")


colnames(dates) = c("Country", "Start interviews Round 7", "End interviews Round 7")


stargazer(as.data.frame(dates), summary=FALSE, rownames = F, out="~/Dropbox/Apps/Overleaf/AfricaOutages/appendix-A1.tex", float=F)
```

2a. IODA data overview
```{r}
#Extract start date and time (change from UTC time stamp)
ioda.data$start <- as_datetime(ioda.data$start, origin = lubridate::origin)

ioda.data$startday <- format(ioda.data$start, "%Y-%m-%d")
ioda.data$starttime <- format(ioda.data$start, "%H:%M:%S")
ioda.data$starttime <- hms::as_hms(ioda.data$starttime)

ioda.data$end <- ioda.data$start + ioda.data$duration
ioda.data$endday <- format(ioda.data$end, "%Y-%m-%d")


#Modify duration variable to hours
ioda.data$duration <- ioda.data$duration/3600


#Categorize between outages lasting less than an hour, less than 6hrs, less than 12hrs, less than 24 hrs
ioda.data$dur <- NA
ioda.data$dur[ioda.data$duration <1] <- "less than 1 hour"
ioda.data$dur[ioda.data$duration >=1 & ioda.data$duration <6] <- "more than 1 and less than 6 hours"
ioda.data$dur[ioda.data$duration >=6 & ioda.data$duration <12] <- "more than 6 and less than 12 hours"
ioda.data$dur[ioda.data$duration >=12 & ioda.data$duration <24] <- "more than 12 and less than 24 hours"
ioda.data$dur[ioda.data$duration >=24] <- "more than 24 hours"


positions <- c("less than 1 hour", "more than 1 and less than 6 hours", "more than 6 and less than 12 hours", "more than 12 and less than 24 hours", "more than 24 hours")
```

```{r}
pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/figure-F1.pdf"), width=7,height=4,paper='special')
ggplot(ioda.data, aes(x=dur)) +
  geom_bar(stat = 'count', width = 0.5,) +
  scale_x_discrete(limits = positions) +
  theme_minimal() +
  theme(aspect.ratio = .5) +
  xlab('') +
  ylab('') + 
  coord_flip()
dev.off()
```

```{r}
ioda.data$country_code <- substring(ioda.data$location, 18,19)
ioda.data$country_name <- countrycode(ioda.data$country_code, origin = 'iso2c', destination ='country.name')

#add ID
ioda.data <- ioda.data %>%                         
  mutate(ID = row_number())
```

Manual changing of region names to match with codes from IODA
```{r}
ioda.data$location_name <- ioda.data$location_name %>%
  str_replace_all(c("Kadiogo" = "Centre",
                    "Praia" = "Santiago-Praia",
                    "Atsimo-Andrefana" = "Atsimo Andrefana",
                    "Mzimba" = "Northern Region", 
                    "Lilongwe" = "Central Region",
                    "Mangochi" = "Southern Region",
                    "Zomba" = "Southern Region",
                    "Blantyre" = "Southern Region",
                    "Beau Bassin-Rose Hill" = "Plaine Wilhems",
                    "Quatre Bornes" = "Plaine Wilhems",
                    "Rivière Noire" = "Black River",
                    "Zambezia" = "Zambézia",
                    "Thiès" = "Thies",
                    "Orange Free State" = "Free State",
                    "KwaZulu-Natal" = "Kwazulu Natal",
                    "Kassala" = "East",
                    "Dar-Es-Salam" = "Dar Es Salam",
                    "Zanzibar West" = "Mjini Magharibi"))


###differentiate between Maputo City and Province
map1 <- ioda.data %>%
  filter(location_code == 2818)

map1$location_name <- map1$location_name %>%
  str_replace_all(c("Maputo" = "Maputo City"))

map2 <- ioda.data %>%
  filter(location_code == 2819)

map2$location_name <- map2$location_name %>%
  str_replace_all(c("Maputo" = "Maputo Province"))

ioda.data <- ioda.data %>%
  filter(!location_name=="Maputo")

ioda.data <- rbind(ioda.data, map1, map2)

###collapse Kavango-West and Kavango-East to Kavango
kav1 <- ioda.data %>%
  filter(location_name=="Kavango")

kav1$location_name <- kav1$location_name %>%
  str_replace_all(c("Kavango" = "Kavango West"))

kav2 <- ioda.data %>%
  filter(location_name=="Kavango")

kav2$location_name <- kav2$location_name %>%
  str_replace_all(c("Kavango" = "Kavango East"))

ioda.data <- ioda.data %>%
  filter(!location_name=="Kavango")
ioda.data <- rbind(ioda.data, kav1, kav2)

###change region name in Sierra Leone
sl <- ioda.data %>%
  filter(country_name=="Sierra Leone")

sl$location_name <- sl$location_name %>%
  str_replace_all(c("Western" = "Western Area"))

ioda.data <- ioda.data %>%
  filter(!country_name=="Sierra Leone")

ioda.data <- rbind(ioda.data, sl)

rm(kav1, kav2, map1, map2, sl)
                  
```
2b. Prepare IODA data for merging:
```{r}
###Select only the largest outages
ioda.data <- ioda.data %>%
  filter(dur=="more than 24 hours")

###Select only those outages where the starting point of the interviews does not fall with the beginning of the interviews. Otherwise, all people would have experienced an outage event before the interviews even took place  and there would be no pre-treated individuals.

###keep a list of treated regions from the beginning - those regions will be excluded later from the sample as they are 'contaminated' with the experience of an outage event
names(dates) <- c("country_name", "startintv", "endintv")
ioda.data <- left_join(ioda.data, dates, by = "country_name")

###drop those cases where the beginning of the outage falls on the same day with the beginning of the interviews 
ioda.data$drop <- ifelse(ioda.data$startday==ioda.data$startintv | ioda.data$startday==ioda.data$endintv,  TRUE, FALSE)

###keep dropped cases 
drop.list <- ioda.data %>%
  dplyr::filter(drop==TRUE) %>%
  dplyr::select(location_name, country_name, drop)

drop.list <- drop.list %>% filter(!location_name=="Eastern Cape")

ioda.data <- ioda.data %>%
  dplyr::filter(drop==FALSE)

###drop IODA cases where regional description is too broadly defined (e.g. northern region)
###I do not have geo-coded data on the location of outages by CAIDA
ioda.data <- ioda.data %>%
  dplyr::filter(!country_name=="Malawi")

###Countries experienced outages in multiple regions a) at the same time and b) at different points in time. Group IODA data by country and startday to get an overview. 
group <- ioda.data %>%
  dplyr::group_by(country_name, startday) %>%
  count() %>%
  mutate(multiple = ifelse(n>1, TRUE, FALSE))  

group <- as.data.frame(group)
group <- group %>% mutate(group_id=row_number())

ioda.data <- left_join(ioda.data, group, by=c("country_name", "startday"))

###drop outages which occur for a second time in the same region (otherwise I would assign individuals to the pre-treatment group which would have already experienced an outage)
ioda.data$location_name[duplicated(ioda.data$location_name)]

ioda.data <- ioda.data %>%
  dplyr::filter(!group_id==8 & !group_id==10  & !group_id==6 & !group_id==13 & !group_id==24 & !group_id==18 & !location_name=="Kavango West")



```


Merge data: merge every outage with the sample of the respective country


```{r}
sample <- full_join(afro.data, ioda.data, by="country_name")

###drop countries which have not experienced Internet outages
sample <- sample %>% drop_na(datasource)

```
Individual selection for Tunisia (use geocoded data)

```{r}
tun <- read.csv("geo-code/r7-geocode/TUN_R7.Data_7Feb19_release.w.local.info.csv")
tun <- tun %>%
  dplyr::select(RESPNO, EA_GPS_LA, EA_GPS_LO, EA_GPS_OTHER) %>%
  separate(EA_GPS_OTHER, c("col1", "col2"), ",")

tun$EA_GPS_LA <- ifelse(is.na(tun$EA_GPS_LA), tun$col1,tun$EA_GPS_LA)
tun$EA_GPS_LO <- ifelse(is.na(tun$EA_GPS_LO), tun$col2,tun$EA_GPS_LO)

tun <- tun %>%
  dplyr::select(-col1, -col2) %>%
  rename(respno = RESPNO, latitude = EA_GPS_LA, longitude = EA_GPS_LO)

summary(tun)


tun <- left_join(sample, tun, by="respno")

tun <- tun %>%
  filter(country_name=="Tunisia") 

tun$latitude <- as.numeric(tun$latitude)
tun$longitude <- as.numeric(tun$longitude)



tun <- tun %>%
  drop_na(longitude, latitude)


tun <- st_as_sf(tun, coords = c("longitude", "latitude"), crs = 4326)


#load afriadmin data (includes polygons of regions in Tunisia)
tunisia <- afriadmin("tunisia", level=1)

joined_tun <- st_join(tun, tunisia)
table(joined_tun$shapeName)

#shapeName replaces region
joined_tun$region_name <- joined_tun$shapeName
joined_tun$region <- joined_tun$shapeISO

joined_tun$region <- joined_tun$region %>% stringr::str_remove("TN-")
joined_tun$region <- as.numeric(joined_tun$region)

joined_tun <- st_drop_geometry(joined_tun)

joined_tun <- joined_tun %>%
  dplyr::select(-shapeName, -shapeISO, -shapeID, -shapeGroup, -shapeType)

sample <- sample %>%
  dplyr::filter(!country_code=="TN")

sample <- rbind(sample, joined_tun)

rm(joined_tun, tun, tunisia)
```

Assign to different groups if a) outages occur at the same time in different regions, all individuals are put into the treatment group of time frame
```{r}
###Drop all regions which have experienced an outage event before interviews took place
names(drop.list)[1] <- "region_name"
sample <- dplyr::left_join(sample, drop.list, by=c("region_name", "country_name"))
sample <- sample %>%
  dplyr::filter(is.na(drop.y))
```

Assign treated individuals
```{r}
sample$treat <- ifelse(sample$region_name==sample$location_name,1,0)
```

Assign pre- and post treatment phases (different for each individual outage)
```{r}
sample <- sample %>%
  dplyr::group_by(ID) %>%
  dplyr::mutate(post = ifelse(day>=startday,1,0))
```

Check for observations within countries (drop countries without pre-treated or post-treated observations)
```{r}
table(sample$country_name, sample$treat, sample$post)
sample <- sample %>%
  dplyr::filter(!country_name=="Sudan" & !country_name=="Tanzania" & !country_name=="Namibia")

```


Collapse those regions which experience an Internet outage around the same time (treat Internet outages in multiple regions as one when occurring at the same time)
```{r}
ov <- sample %>%
  dplyr::group_by(ID) %>%
  dplyr::summarise(startday=startday, country_name=country_name, region_name=region_name, treat=treat, multiple=multiple, region=region) %>%
  dplyr::distinct() %>%
  dplyr::filter(treat==1)

ov <- ov %>%
  dplyr::group_by() %>%
  dplyr::select(-ID,-treat, -multiple, -region)

colnames(ov) = c("Date", "Country", "Region")

```

```{r}
sample$region <- as.numeric(sample$region)
sample <- sample %>%
  dplyr::filter(!ID==3 #drop region 'Central' in Ghana (outage at the same time as in Ashanti)
         & !ID==32 #drop region 'Eastern' in Kenya (outage at the same time as in Nairobi)
         & !ID==42 & !ID==43 #drop regions 'Atsimo Adrefana' and 'Diana' from Madagascar 
         & (!(region==543 & ID==94)) #drop Sofala from Inhambane case (Mozambique)
         & (!(region==544 & ID==117))#(drop Inhambane from Sofala case (Mozambique))
        & !ID==133 #drop Grand Port in Mauritius (outage at the same time in Plaine Wilhems)
        & !ID==501 #drop Siliana from Beja Tunisia (case from 2018-04-01)
        & (!(region==31 & ID==495)) #drop Beja from Siliana case
        & (!(region==21 & ID==495)) #drop Nabeul from Siliana case
        & (!(region==71 & ID==495)) #drop Gafsa from Siliana case
        & (!(region==61 & ID==495)) #drop Sfax from Siliana case
        & (!(region==52 & ID==495)) #drop Monastir from Siliana case
        & !ID==495 & !ID==498 & !ID==499 & !ID==502 #drop Gafsa, Monastir, Nabeul, Sfax from Tunisia (occurrence of outage in Beja at the same time) 
        & (!(region==32 & ID==493)) #drop Jendouba from Beja case (case from 2018-04-17)
        & !ID==497 #drop Tunis case (Tunisia)
        & (!(region==705 & ID==548)) #drop Mpumalanga from North West case (South Africa)
        & (!(region==706 & ID==558)) #drop North West from Mpumalanga case (South Africa)
        & (!(region==700 & ID==558)) #drop Eastern Cape case from Mpumalanga case (South Africa)
        & !ID==566) #drop Eastern Cape case (together with North West case)

sample <- sample %>% 
  dplyr::mutate(treat = replace(treat, region == 261, 1), #assign individuals from Central (Ghana)
         treat = replace(treat, region == 302, 1), #assign individuals from Eastern (Kenya)
         treat = replace(treat, region == 426, 1), #assign individuals from Atsimo Andrefana(Madagascar)
         treat = replace(treat, region == 432, 1), #assign individuals from Diana (Madagascar)
         treat = replace(treat, region == 904, 1), #assign individuals from Grand Port (Mauritius)
         treat = replace(treat, region == 34, 1),
         treat = replace(treat, region_name == "Siliana", 1),
         treat = replace(treat, region_name == "Gafsa", 1),
         treat = replace(treat, region_name == "Monastir", 1),
         treat = replace(treat, region_name == "Nabeul", 1),
         treat = replace(treat, region_name == "Sfax", 1),
         treat = replace(treat, region == 700, 1)) #assign individuals from Eastern Cape (South Africa)

table(sample$post, sample$treat)
```

```{r}
#Overview by country
table(sample$country_code)

mz <- sample %>% filter(country_code=="MZ")
table(mz$treat, mz$post, mz$region_name) #Inhambane no post-treated individuals (sole case might drop ID 117)

za <- sample %>% filter(country_code=="ZA")
table(za$treat, za$post, za$region_name) #Mpumalanga no post-treated individuals (sole case ID 558)

#drop cases with no post-treated individuals
sample <- sample %>% filter(!ID==117 & !ID==558)

ov <- ov %>% filter(!Region=="Inhambane" & !Region=="Mpumalanga")

stargazer(as.data.frame(ov), summary=FALSE, rownames = F, out="~/Dropbox/Apps/Overleaf/AfricaOutages/appendix-A2.tex", float = F)
```



Add population data
```{r}
pop <- read_excel("Data_Extract_From_Subnational_Population.xlsx")

pop <- pop %>%
  dplyr::select(`Country Name`,`2016 [YR2016]`) %>%
  drop_na() %>%
  separate('Country Name', paste("Country Name", 1:2, sep="_"), sep=",", extra="drop") %>%
  rename(country_name='Country Name_1', region_name='Country Name_2', pop='2016 [YR2016]')

pop$region_name <- str_replace_all(pop$region_name, " ", "")

sample <- left_join(sample, pop, by = c("country_name", "region_name"))
```

Add prior outages
```{r}
prior <- read.csv("prior_outages/prior.csv")
prior <- prior %>%
  dplyr::select(-country_name)

sample <- left_join(sample, prior, by="location_name")

```

```{r}
###save as csv file
write.csv(sample,"afro-sample-v2.csv", row.names = F)

```

Visualization Maps
```{r}

###Ghana
gha <- afriadmin("ghana", level=1)
gha$treat <- 0
gha <- gha %>%
  mutate(treat = replace(treat, shapeName=="Ashanti",1),
         treat = replace(treat, shapeName=="Central",1),
         treat = replace(treat, shapeName=="Greater Accra",NA))
tm_gha <-tm_shape(gha) +
  tm_polygons("treat", palette="Greys") +
  tm_layout(title="Ghana", legend.show=F)
tmap_save(tm_gha, "~/Dropbox/Apps/Overleaf/AfricaOutages/map-ghana.png", width=1920, height=1080, asp=0)


###Kenya
ken <- st_read(file.path("kenya_region_shapefile.shp"), crs=4326)
table(ken$name_1)
ken$treat <- 0
ken <- ken %>%
  mutate(treat = replace(treat, name_1=="Nairobi",1),
         treat = replace(treat, name_1=="Eastern",1))
tm_ken <-tm_shape(ken) +
  tm_polygons("treat", palette="Greys") +
  tm_layout(title="Kenya", legend.show=F)
tmap_save(tm_ken, "~/Dropbox/Apps/Overleaf/AfricaOutages/map-kenya.png", width=1920, height=1080, asp=0)



###Madagascar 
mad <- afriadmin("madagascar", level=1)
mad$treat <- 0
table(mad$shapeName)
mad <- mad %>%
  mutate(treat = replace(treat, shapeName=="Analamanga",1),
         treat = replace(treat, shapeName=="Atsimo Andrefana",1),
         treat = replace(treat, shapeName=="Diana",1))
tm_mad <-tm_shape(mad) +
  tm_polygons("treat", palette="Greys") +
  tm_layout(title="Madagascar", legend.show=F)
tmap_save(tm_mad, "~/Dropbox/Apps/Overleaf/AfricaOutages/map-madagascar.png", width=1920, height=1080, asp=0)

###Mozambique 
moz <- afriadmin("mozambique", level=1)
moz$treat <- 0
table(moz$shapeName)
moz <- moz %>%
  mutate(treat = replace(treat, shapeName=="Sofala",1),
         treat = replace(treat, shapeName=="Inhambane",NA))
tm_moz <-tm_shape(moz) +
  tm_polygons("treat", palette="Greys") +
  tm_layout(title="Mozambique", legend.show=F)
tmap_save(tm_moz, "~/Dropbox/Apps/Overleaf/AfricaOutages/map-mozambique.png", width=1920, height=1080, asp=0)

###Mauritius 
mau <- afriadmin("mauritius", level=1)
table(mau$shapeName)
mau$treat <- 0
mau <- mau %>%
  mutate(treat = replace(treat, shapeName=="Grand Port",1),
         treat = replace(treat, shapeName=="Plaines Wilhems",1),
         treat = replace(treat, shapeName=="Black River",NA))
tm_mau <-tm_shape(mau) +
  tm_polygons("treat", palette="Greys") +
  tm_layout(title="Mauritius", legend.show=F)
tmap_save(tm_mau, "~/Dropbox/Apps/Overleaf/AfricaOutages/map-mauritius.png", width=1920, height=1080, asp=0)

###Senegal 
sen <- afriadmin("senegal", level=1)
table(sen$shapeName)
sen$treat <- 0
sen <- sen %>%
  mutate(treat = replace(treat, shapeName=="Thies",1),
         treat = replace(treat, shapeName=="Kedougou",NA),
         treat = replace(treat, shapeName=="Ziguinchor",NA))
tm_sen <-tm_shape(sen) +
  tm_polygons("treat", palette="Greys") +
  tm_layout(title="Senegal", legend.show=F)
tmap_save(tm_sen, "~/Dropbox/Apps/Overleaf/AfricaOutages/map-senegal.png", width=1920, height=1080, asp=0)

###Tunisia 
tun <- afriadmin("tunisia", level=1)
table(tun$shapeName)
tun$treat <- 0
tun1 <- tun %>%
  mutate(treat = replace(treat, shapeName=="Jendouba",1),
         treat = replace(treat, shapeName=="Siliana",1),
         treat = replace(treat, shapeName=="Tunis",NA),
         treat = replace(treat, shapeName=="Béja",NA),
         treat = replace(treat, shapeName=="Gafsa",NA),
         treat = replace(treat, shapeName=="Monastir",NA),
         treat = replace(treat, shapeName=="Nabeul",NA),
         treat = replace(treat, shapeName=="Sfax",NA))
tm_tun1 <-tm_shape(tun1) +
  tm_polygons("treat", palette="Greys") +
  tm_layout(title="Tunisia", legend.show=F)
tmap_save(tm_tun1, "~/Dropbox/Apps/Overleaf/AfricaOutages/map-tunisia1.png", width=1920, height=1080, asp=0)

tun2 <- tun %>%
  mutate(treat = replace(treat, shapeName=="Jendouba",NA),
         treat = replace(treat, shapeName=="Siliana",NA),
         treat = replace(treat, shapeName=="Tunis",NA),
         treat = replace(treat, shapeName=="Béja",1),
         treat = replace(treat, shapeName=="Gafsa",1),
         treat = replace(treat, shapeName=="Monastir",1),
         treat = replace(treat, shapeName=="Nabeul",1),
         treat = replace(treat, shapeName=="Sfax",1))
tm_tun2 <-tm_shape(tun2) +
  tm_polygons("treat", palette="Greys") +
  tm_layout(title="Tunisia", legend.show=F)
tmap_save(tm_tun2, "~/Dropbox/Apps/Overleaf/AfricaOutages/map-tunisia2.png", width=1920, height=1080, asp=0)

###South Africa  
sa <- afriadmin("south africa", level=1)
table(sa$shapeName)
sa$treat <- 0
sa <- sa %>%
  mutate(treat = replace(treat, shapeName=="North West",1),
         treat = replace(treat, shapeName=="Eastern Cape",1),
         treat = replace(treat, shapeName=="Mpumalanga", NA))
         
tm_sa <-tm_shape(sa) +
  tm_polygons("treat", palette="Greys") +
  tm_layout(title="South Africa", legend.show=F)
tmap_save(tm_sa, "~/Dropbox/Apps/Overleaf/AfricaOutages/map-southafrica.png", width=1920, height=1080, asp=0)




```
