---
title: "afro-analysis-24.05.22"
author: "Rebecca Strauch"
date: "5/24/2022"
output: html_document
---

---
title: "africa-analysis-exact"
author: "Rebecca Strauch"
date: "7/9/2021"
output: html_document
---
Data Analysis for "How Internet outages shape government evaluation in Africa"
Rebecca Strauch
02.07.2021

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages and data
```{r}
rm(list=ls())
library(lubridate)
library(stargazer)
library(tidyverse)
library(coefplot)
library(janitor)
library(WeightIt)
library(cobalt)
library(dgof)
library(sampling)
library(lmtest)
library(sandwich)

#Load datafile
sample <- read.csv("afro-sample.csv")

```



Modifications
```{r}
table(sample$treat, sample$post)
###Social desirability bias: create dichotomous variable (of variables of interest) with assigned non-responses

###Assign Don't know or missing answers to NA
sample$non_resp_trst_pres <- ifelse(sample$trst_pres==8 | sample$trst_pres==9,1,0)
table(sample$non_resp_trst_pres)
sample$trst_pres[sample$trst_pres==8] <- NA
sample$trst_pres[sample$trst_pres==9] <- NA
table(sample$trst_pres)

sample$non_resp_trst_parl <- ifelse(sample$trst_parl==8 | sample$trst_parl==9,1,0)
table(sample$non_resp_trst_parl)
sample$trst_parl[sample$trst_parl==-1] <- NA
sample$trst_parl[sample$trst_parl==8] <- NA
sample$trst_parl[sample$trst_parl==9] <- NA
table(sample$trst_parl)

sample$non_resp_trst_local <- ifelse(sample$trst_local==8 | sample$trst_local==9,1,0)
table(sample$non_resp_trst_local)
sample$trst_local[sample$trst_local==8] <- NA
sample$trst_local[sample$trst_local==9] <- NA
table(sample$trst_local)

sample$trst_opposition[sample$trst_opposition==8] <- NA
sample$trst_opposition[sample$trst_opposition==9] <- NA
sample$trst_opposition[sample$trst_opposition==-1] <- NA
table(sample$trst_opposition)

sample$non_resp_perf_pres <- ifelse(sample$perf_pres==8 |sample$perf_pres==9,1,0)
table(sample$non_resp_perf_pres)
sample$perf_pres[sample$perf_pres==-1] <- NA
sample$perf_pres[sample$perf_pres==8] <- NA
sample$perf_pres[sample$perf_pres==9] <- NA
sample$perf_pres[sample$perf_pres==1] <- 0
sample$perf_pres[sample$perf_pres==2] <- 1
sample$perf_pres[sample$perf_pres==3] <- 2
sample$perf_pres[sample$perf_pres==4] <- 3
table(sample$perf_pres)

sample$non_resp_perf_parl <- ifelse(sample$perf_parl==8 |sample$perf_parl==9,1,0)
table(sample$non_resp_perf_parl)
sample$perf_parl[sample$perf_parl==-1] <- NA
sample$perf_parl[sample$perf_parl==8] <- NA
sample$perf_parl[sample$perf_parl==9] <- NA
sample$perf_parl[sample$perf_parl==1] <- 0
sample$perf_parl[sample$perf_parl==2] <- 1
sample$perf_parl[sample$perf_parl==3] <- 2
sample$perf_parl[sample$perf_parl==4] <- 3
table(sample$perf_parl)

sample$non_resp_perf_local <- ifelse(sample$perf_local==8 |sample$perf_local==9,1,0)
table(sample$non_resp_perf_local)
sample$perf_local[sample$perf_local==-1] <- NA
sample$perf_local[sample$perf_local==8] <- NA
sample$perf_local[sample$perf_local==9] <- NA
sample$perf_local[sample$perf_local==99] <- NA
sample$perf_local[sample$perf_local==1] <- 0
sample$perf_local[sample$perf_local==2] <- 1
sample$perf_local[sample$perf_local==3] <- 2
sample$perf_local[sample$perf_local==4] <- 3
table(sample$perf_local)

sample$non_resp_democr <- ifelse(sample$democr==8 |sample$democr==9,1,0)
table(sample$non_resp_democr)
sample$democr[sample$democr==8] <- NA
sample$democr[sample$democr==9] <- NA
sample$democr[sample$democr==0] <- NA
sample$democr[sample$democr==1] <- 0
sample$democr[sample$democr==2] <- 1
sample$democr[sample$democr==3] <- 2
sample$democr[sample$democr==4] <- 3
table(sample$democr)

sample$age[sample$age==998] <- NA
sample$age[sample$age==999] <- NA
table(sample$age)

sample$female[sample$female==1] <- 0
sample$female[sample$female==2] <- 1
table(sample$female)

sample$housing[sample$housing==-1] <- NA
sample$housing[sample$housing==7] <- NA
sample$housing[sample$housing==8] <- NA
sample$housing[sample$housing==1] <- 0
sample$housing[sample$housing==2] <- 1
sample$housing[sample$housing==3] <- 2
sample$housing[sample$housing==4] <- 3
sample$housing[sample$housing==5] <- 4
table(sample$housing)


#sample$non_resp_perf_parl <- ifelse(is.na(sample$perf_parl),1,0)
#sample$non_resp_perf_local <- ifelse(is.na(sample$perf_local),1,0)



```




Interview time frames sorted by region
```{r}
###Regional interview dates
region_dates <- sample%>%
   summarise(country_name = country_name, region_name = region_name, startintv = startintv.x, endintv = endintv.x)%>%
  distinct() %>%
  arrange(country_name, region_name) %>%
  drop_na()

colnames(region_dates) = c("Country", "Region", "Start interview (region)", "End interview (region)")

stargazer(as.data.frame(region_dates), summary=FALSE, rownames = F,
          #out="~/Dropbox/Apps/Overleaf/AfricaOutages/appendix-A3.tex", float = F)

  
```




Overview of individual assignments
```{r}
table(sample$post, sample$treat)

s <- sample
s$treat <- ifelse(s$treat==1,"Treatment","Control")
s$post <- ifelse(s$post==1,"Post","Pre")

table(s$post, s$treat)

t <- s %>% tabyl(treat, post)

colnames(t) = c("", "Post", "Pre")

t <- t %>%
  relocate(Pre, .before = Post) %>%
  drop_na()

stargazer(as.data.frame(t), summary=FALSE, rownames = F,
          out="~/Dropbox/Apps/Overleaf/AfricaOutages/table-T1.tex", float = F)
```

Balance test for demographic variables
```{r}

x <- sample %>% filter(treat==0) %>% dplyr::select(age, housing, female)
y <- sample %>% filter(treat==1) %>% dplyr::select(age, housing, female)
ks.test(x$age,y$age)
ks.test(x$housing,y$housing)
ks.test(x$female,y$female)

#Visualization
cov <- sample %>% dplyr::select(treat,age, housing, female) %>%
  drop_na() 
data <- cov %>% dplyr::select(treat)
cov <- cov %>% dplyr::select(-treat)


W.out <- weightit(treat ~ cov, data = data,
                  method = "ps", estimand = "ATT")

bal.tab(W.out)

pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/appendix-A4.pdf"), width=7,height=4,paper='special')
bal.plot(W.out, var.name = "age", which = "unadjusted")
dev.off()

pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/appendix-A5.pdf"), width=7,height=4,paper='special')
bal.plot(W.out, var.name = "housing", which = "unadjusted")
dev.off()

#pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/female.pdf"), width=7,height=4,paper='special')
#bal.plot(W.out, var.name = "female", which = "unadjusted")
#dev.off()
```



```{r}
#create time-pending variable 
#month
sample$month <- format(as.Date(sample$day), "%Y-%m")
#week
sample$week <- strftime(sample$day, format = "%Y-%V")
```

Analysis
```{r}

###1. Hypothesis: Effect of outages on variables of interest
stargazer(lm(perf_pres ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample),
          lm(perf_parl ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample),
          lm(perf_local ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), sample),
          lm(democr ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), sample), 
          lm(trst_pres ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), sample),
          lm(trst_parl ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), sample),
          lm(trst_local ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample),
          title="Model 1",
          type="text",
          out="~/Dropbox/Apps/Overleaf/AfricaOutages/model1.tex",
          float = F,
          omit="as.factor",
          omit.stat = c("ser", "f"),
          dep.var.labels = c("Performance of president", "Performance of parliament", "Performance of local council", "Satisfaction with democracy", "Trust in president", "Trust in parliament", "Trust in local council"),
          covariate.labels = c("Treatment", "Post", "Age", "Housing", "Treatment*Post"),
          add.lines = list(c("Region FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Week FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")))
```


2. Hypothesis: Use 3 models expanding over 30 days after the outage.
Always include the control group and then add day 1-10 to the analysis (followed by days 11-20, and 21 to 30.)
```{r}
###2. Hypothesis: Negative effect of outages on trust is more prominent around days of outage
###Create difference in time from event 
sample$difference <- difftime(sample$day, sample$startday, units = c("days"))


sample10 <- sample %>%
  filter(difference<=10)

sample20 <- sample %>%
  filter(difference<=0 | difference>=11)

sample20 <- sample20 %>%
  filter(difference <=20)

sample30 <- sample %>%
  filter(difference<=0 |  difference>=21)

sample30 <- sample30 %>%
  filter(difference<=30)


stargazer(lm(trst_pres ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample10),
          lm(trst_pres ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample20),
          lm(trst_pres ~ treat + post + treat*post + age + housing + as.factor(region)+ as.factor(week), sample30),lm(trst_parl ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample10),
          lm(trst_parl ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample20),
          lm(trst_parl ~ treat + post + treat*post + age + housing + as.factor(region)+ as.factor(week), sample30),
          lm(trst_local ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample10),
          lm(trst_local ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample20),
          lm(trst_local ~ treat + post + treat*post + age + housing + as.factor(region)+ as.factor(week), sample30),
          title="Internet outages on trust in president (10, 20, 30 days frame)",
          type="text",
          out="~/Dropbox/Apps/Overleaf/AfricaOutages/trust2.tex",
          float = F,
          omit="as.factor",
          omit.stat = c("ser", "f"),
          covariate.labels = c("Treatment", "Post", "Age", "Housing", "Treatment*Post"),
          dep.var.labels = c("Trust in president", "Trust in parliament", "Trust in local council"),
          column.labels   = c("10 days", "11 to 20 days", "21 to 30 days", "10 days", "11 to 20 days", "21 to 30 days", "10 days", "11 to 20 days", "21 to 30 days"),
          add.lines = list(c("Region FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Week FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")))



```

```{r}
#Temporal effect of outages on performance
stargazer(lm(perf_pres ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample10),
          lm(perf_pres ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample20),
          lm(perf_pres ~ treat + post + treat*post + age + housing + as.factor(region)+ as.factor(week), sample30),
          lm(perf_parl ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample10),
          lm(perf_parl ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample20),
          lm(perf_parl ~ treat + post + treat*post + age + housing + as.factor(region)+ as.factor(week), sample30),
          lm(perf_local ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample10),
          lm(perf_local ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample20),
          lm(perf_local ~ treat + post + treat*post + age + housing + as.factor(region)+ as.factor(week), sample30),
          lm(democr ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample10),
          lm(democr ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), sample20),
          lm(democr ~ treat + post + treat*post + age + housing + as.factor(region)+ as.factor(week), sample30),
          title="Internet outages on performance of president, parliament and council (10, 20, 30 days frame)",
          out="~/Dropbox/Apps/Overleaf/AfricaOutages/model2.tex",
          type="text",
          float = F,
          omit="as.factor",
          omit.stat = c("ser", "f"),
          covariate.labels = c("Treatment", "Post", "Age", "Housing", "Treatment*Post"),
          dep.var.labels = c("Performance of president", "Performance of parliament", "Performance of local council", "Satisfaction with democracy"),
          column.labels   = c("10 days", "11 to 20 days", "21 to 30 days", "10 days", "11 to 20 days", "21 to 30 days", "10 days", "11 to 20 days", "21 to 30 days"),
          add.lines = list(c("Region FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes","Yes", "Yes", "Yes"),
                           c("Week FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes","Yes", "Yes", "Yes")))

```

Interaction with trust in opposition
```{r}
stargazer(lm(perf_pres ~ treat + post + trst_opposition + age + housing + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          lm(perf_parl ~ treat + post + trst_opposition + age + housing + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          lm(perf_local ~ treat + post + trst_opposition + age + housing + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          lm(democr ~ treat + post + trst_opposition + age + housing + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          lm(trst_pres ~ treat + post + trst_opposition + age + housing + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          lm(trst_parl ~ treat + post + trst_opposition + age + housing  + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          lm(trst_local ~ treat + post + trst_opposition + age + housing  + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          title="Interaction term with party affiliation",
          out="~/Dropbox/Apps/Overleaf/AfricaOutages/model3.tex",
          type="text",
          float = F,
          omit="as.factor",
          omit.stat = c("ser", "f"),
          dep.var.labels = c("Performance of president", "Performance of parliament", "Performance of local council", "Satisfaction with democracy", "Trust in president", "Trust in parliament", "Trust in local council"),
          covariate.labels = c("Treatment","Post", "Opposition", "Age", "Housing", "Treatment*Post", "Treatment*Opposition", "Post*Opposition", "Treatment*Post*Opposition"),
          add.lines = list(c("Region FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Week FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes","Yes")))



```

```{r}

pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/figure-F2.pdf"), width=7,height=4,paper='special')
multiplot(lm(perf_pres ~ treat + post + trst_opposition + age + housing + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          lm(perf_parl ~ treat + post + trst_opposition + age + housing + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          lm(perf_local ~ treat + post + trst_opposition + age + housing + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          lm(democr ~ treat + post + trst_opposition + age + housing + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          lm(trst_pres ~ treat + post + trst_opposition + age + housing + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          lm(trst_parl ~ treat + post + trst_opposition + age + housing  + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          lm(trst_local ~ treat + post + trst_opposition + age + housing  + treat*post*trst_opposition + as.factor(region) + as.factor(week), sample),
          outerCI = 1.645,
          coefficients = c("treat:post:trst_opposition"), horizontal=F) +
  scale_color_brewer(name="Dependent variable", palette = "Blues", labels=c("Satisfaction with democracy", "Performance of local council",  "Performance of parliament", "Performance of president","Trust in local council",  "Trust in parliament", "Trust in president"))  + scale_y_discrete(labels = c("")) + theme_minimal() +
  xlab("Coefficient estimate") + ylab("") + theme(
  plot.title = element_blank())
dev.off()



```



Visualizations
```{r}
vis <- sample %>% 
  group_by(day,country_name) %>% 
  summarize(trst_pres=mean(trst_pres, na.rm = TRUE), 
            trst_parl=mean(trst_parl, na.rm = TRUE),
            trst_local=mean(trst_local, na.rm = TRUE),
            perf_pres=mean(perf_pres, na.rm = TRUE),
            perf_parl=mean(perf_parl, na.rm = TRUE),
            perf_local=mean(perf_local, na.rm = TRUE),
            democr=mean(democr, na.rm = TRUE))
vis$day <- as.Date(vis$day)

pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/timeline_trust.pdf"), width=7,height=4,paper='special')
ggplot(vis, aes(x = day)) +
  geom_line(aes(y = trst_pres, linetype = "trst_pres")) +
  geom_line(aes(y = trst_parl, linetype = "trst_parl")) +
  geom_line(aes(y = trst_local, linetype = "trst_local")) +
  scale_color_manual(values = c("trst_pres"="dashed", "trst_parl"="twodash", 
                                 "trst_local"="dotted")) +
  scale_fill_manual(labels = c("trst_local"="Local government", "trst_parl"="Parliament", "trst_pres"="President")) +
  xlab('Date') +
  ylab('Trust in government institutions') +
  facet_wrap(~country_name, scales = "free_x") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
dev.off()

pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/timeline_performance.pdf"), width=7,height=4,paper='special')
ggplot(vis, aes(x = day)) +
  geom_line(aes(y = trst_pres, linetype = "perf_pres")) +
  geom_line(aes(y = trst_parl, linetype = "perf_parl")) +
  geom_line(aes(y = trst_local, linetype = "perf_local")) +
  geom_line(aes(y = democr, linetype = "democr")) +
  scale_color_manual(values = c("democr"="solid", "perf_parl"="dashed", 
                                 "perf_parl"="twodash", "perf_local"="dotted")) +
  scale_fill_manual(labels = c("democr"="Democracy", "perf_local"="Local government", "perf_parl"="Parliament", "perf_pres"="President")) +
  xlab('Date') +
  ylab('Performance of government institutions') +
  facet_wrap(~country_name, scales = "free_x") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
dev.off()




```

Social desirability bias: If repression works, then respondents are more likely to give non-responses than to express their dissatisfaction with the current government. Thus, I apply a logit regression with a dichotomous variable with (1) all values of NA, and (0) otherwise.
```{r}
library(survival)

stargazer(clogit(non_resp_perf_pres ~ treat + post + treat*post + age + housing + strata(region) + as.factor(week), sample, method="efron"),
          clogit(non_resp_perf_parl ~ treat + post + treat*post + age + housing + strata(region) + as.factor(week), sample, method="efron"),
          clogit(non_resp_perf_local ~ treat + post + treat*post + age + housing + strata(region) + as.factor(week), sample, method="efron"),
          clogit(non_resp_democr ~ treat + post + treat*post +  age + housing +  strata(region) + as.factor(week), sample, method="efron"),
          clogit(non_resp_trst_pres ~ treat + post + treat*post + age + housing + strata(region) + as.factor(week), sample, method="efron"),
          clogit(non_resp_trst_parl ~ treat + post + treat*post + age + housing + strata(region) + as.factor(week), sample, method="efron"),
          clogit(non_resp_trst_local ~ treat + post + treat*post + age + housing + strata(region) + as.factor(week), sample, method="efron"),
          title="Non responses",
          type="text",
          out="~/Dropbox/Apps/Overleaf/AfricaOutages/appendix-A10.tex",
          float = F,
          omit="as.factor",
          omit.stat = c("ser", "f"),
          dep.var.labels = c("Performance of president","Performance of parliament", "Performance of local councilor", "Satisfaction with democracy", "Trust in president", "Trust in parliament", "Trust in local council"),
          covariate.labels = c("Treatment","Post", "Age", "Housing", "Treatment*Post"),
          add.lines = list(c("Region FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Week FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes","Yes")))


stargazer(glm(non_resp_perf_pres ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), family = "binomial", sample),
          glm(non_resp_perf_parl ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), family = "binomial", sample),
          glm(non_resp_perf_local ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), family = "binomial", sample),
          glm(non_resp_democr ~ treat + post + treat*post +  age + housing +  as.factor(region) + as.factor(week), family = "binomial", sample),
          glm(non_resp_trst_pres ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), family = "binomial", sample),
          glm(non_resp_trst_parl ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), family = "binomial", sample),
          glm(non_resp_trst_local ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), family = "binomial", sample),
          title="Non responses",
          type="text",
          out="~/Dropbox/Apps/Overleaf/AfricaOutages/appendix-A10.tex",
          float = F,
          omit="as.factor",
          omit.stat = c("ser", "f", "Max. Possible R2"),
          dep.var.labels = c("Performance of president","Performance of parliament", "Performance of local councilor", "Satisfaction with democracy", "Trust in president", "Trust in parliament", "Trust in local council"),
          covariate.labels = c("Treatment","Post", "Age", "Housing", "Treatment*Post"),
          add.lines = list(c("Region FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Week FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes","Yes")))



```
Check accuracy of IODA data: use subsample of populated places larger than the median split of affected regions
```{r}
summary(sample$pop)

pop <- sample %>%
  filter(pop>2856000) %>%
  summarise(pop = pop, country_name=country_name, region_name=region_name) %>%
  distinct() %>%
  print()

###only select affected regions

subsample <- sample %>%
  filter(country_name==c("Ghana", "Kenya", "Madagascar")) 

stargazer(lm(perf_pres ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), subsample),
          lm(perf_parl ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), subsample),
          lm(perf_local ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), subsample),
          lm(democr ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), subsample), 
          lm(trst_pres ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), subsample),
          lm(trst_parl ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), subsample),
          lm(trst_local ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), subsample),
          title="Population",
          out="~/Dropbox/Apps/Overleaf/AfricaOutages/appendix-A7.tex",
          float = F,
          omit="as.factor",
          omit.stat = c("ser", "f"),
          dep.var.labels = c("Performance of president","Performance of parliament", "Performance of local council", "Satisfaction with democracy", "Trust in president", "Trust in parliament", "Trust in local council"),
          covariate.labels = c("Treatment", "Post", "Age", "Housing", "Treatment*Post"),
          add.lines = list(c("Region FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Week FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")))
  
```


Check: Autocratic countries
```{r}
#subset autocratic states
aut <- sample %>%
  filter(!country_name=="Ghana" & !country_name=="Mauritius" & !country_name=="Senegal" & !country_name=="South Africa")

stargazer(lm(perf_parl ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), aut),
          lm(perf_parl ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), aut),
          lm(perf_local ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), aut),
          lm(democr ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), aut), 
          lm(trst_pres ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), aut),
          lm(trst_parl ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), aut),
          lm(trst_local ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), aut),
          title="Internet outages on trust in president and parliament",
          out="~/Dropbox/Apps/Overleaf/AfricaOutages/appendix-A8.tex",
          float = F,
          omit="as.factor",
          omit.stat = c("ser", "f"),
          dep.var.labels = c("Performance of president","Performance of parliament", "Performance of local council", "Satisfaction with democracy", "Trust in president", "Trust in parliament", "Trust in local council"),
          covariate.labels = c("Treatment", "Post", "Age", "Housing", "Treatment*Post"),
          add.lines = list(c("Region FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Week FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")))
```
Only run analysis for those regions that have NOT experienced such a large outage event three months prior to the survey wave. Here, individuals might not anticipate an outage to occur - in other regions, individuals might already be used to such outages, and an outage during the survey wave might not influence how they regard and evaluate their government.

```{r}
table(sample$prior, sample$region_name)

prior <- sample %>%
  filter(prior==1) %>%
  summarise(prior = prior, region_name = region_name, country_name=country_name) %>%
  distinct() %>%
  print()

ant <- sample %>%
  filter(!country_name=="Ghana" & !country_name=="Mozambique" & !country_name=="Tunisia")



stargazer(lm(perf_pres ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), ant),
          lm(perf_parl ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), ant),
          lm(perf_local ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), ant),
          lm(democr ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), ant), 
          lm(trst_pres ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), ant),
          lm(trst_parl ~ treat + post + treat*post + age + housing+ as.factor(region) + as.factor(week), ant),
          lm(trst_local ~ treat + post + treat*post + age + housing + as.factor(region) + as.factor(week), ant),
          title="Anticipation",
          out="~/Dropbox/Apps/Overleaf/AfricaOutages/appendix-A9.tex",
          float = F,
          omit="as.factor",
          omit.stat = c("ser", "f"),
          dep.var.labels = c("Performance of president","Performance of parliament", "Performance of local council", "Satisfaction with democracy", "Trust in president", "Trust in parliament", "Trust in local council"),
          covariate.labels = c("Treatment", "Post", "Age", "Housing", "Treatment*Post"),
          add.lines = list(c("Region FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Week FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes","Yes")))
```


Pre-test for Parallel Trends Assumption
```{r}
test <- sample %>%
  dplyr::select(trst_pres, trst_parl, trst_local, perf_pres, perf_parl, perf_local, democr, difference, region, week, treat, post) %>%
  filter(difference>-4 & difference<3 & treat==1)
test$Dtmin3 <- ifelse(test$difference==-3, 1, 0)
test$Dtmin2 <- ifelse(test$difference==-2, 1, 0)
test$Dt0 <- ifelse(test$difference==0, 1, 0)
test$Dt1 <- ifelse(test$difference==1, 1, 0)
test$Dt2 <- ifelse(test$difference==2, 1, 0)

stargazer(lm(trst_pres ~ as.factor(region) + as.factor(week) + Dtmin3 + Dtmin2 + Dt0 + Dt1 + Dt2, data=test),
          lm(trst_parl ~ as.factor(region) + as.factor(week) + Dtmin3 + Dtmin2 + Dt0 + Dt1 + Dt2, data=test),
          lm(trst_local ~ as.factor(region) + as.factor(week) + Dtmin3 + Dtmin2 + Dt0 + Dt1 + Dt2, data=test),
          lm(perf_pres ~ as.factor(region) + as.factor(week) + Dtmin3 + Dtmin2 + Dt0 + Dt1 + Dt2, data=test),
          lm(perf_parl ~ as.factor(region) + as.factor(week) + Dtmin3 + Dtmin2 + Dt0 + Dt1 + Dt2, data=test),
          lm(perf_local ~ as.factor(region) + as.factor(week) + Dtmin3 + Dtmin2 + Dt0 + Dt1 + Dt2, data=test),
          lm(democr ~ as.factor(region) + as.factor(week) + Dtmin3 + Dtmin2 + Dt0 + Dt1 + Dt2, data=test),
          title="Testing parallel trends assumption",
          type="text",
          out="~/Dropbox/Apps/Overleaf/AfricaOutages/appendix-A6.tex",
          float = F,
          omit="as.factor",
          omit.stat = c("ser", "f"),
          dep.var.labels = c("Trust in president", "Trust in parliament", "Trust in local council", "Performance of president", "Performance of parliamant", "Performance of local councilor", "Satisfaction with democracy"),
          add.lines = list(c("Region FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Week FEs?", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")))

ps <- sample %>%
  filter(difference>-4 & difference<3)
pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/parallel_1.pdf"), width=7,height=4,paper='special')
ggplot(ps, aes(difference, trst_pres, group = treat, linetype=factor(treat))) +
  stat_summary(geom = 'line') +
  geom_vline(xintercept = 0) +
  scale_linetype_manual(name = "Group", labels=c("Control", "Treatment"), values=c( "dashed", "solid"))+
  xlab("Day") + ylab("Trust in president") +
  theme_minimal()
dev.off()

pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/parallel_2.pdf"), width=7,height=4,paper='special')
ggplot(ps, aes(difference, trst_parl, group = treat, linetype=factor(treat))) +
  stat_summary(geom = 'line') +
  geom_vline(xintercept = 0) +
  scale_linetype_manual(name = "Group", labels=c("Control", "Treatment"), values=c( "dashed", "solid"))+
  xlab("Day") + ylab("Trust in parliament") +
  theme_minimal()
dev.off()

pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/parallel_3.pdf"), width=7,height=4,paper='special')
ggplot(ps, aes(difference, trst_local, group = treat, linetype=factor(treat))) +
  stat_summary(geom = 'line') +
  geom_vline(xintercept = 0) +
  scale_linetype_manual(name = "Group", labels=c("Control", "Treatment"), values=c( "dashed", "solid"))+
  xlab("Day") + ylab("Trust in local council") +
  theme_minimal()
dev.off()

pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/parallel_4.pdf"), width=7,height=4,paper='special')
ggplot(ps, aes(difference, perf_pres, group = treat, linetype=factor(treat))) +
  stat_summary(geom = 'line') +
  geom_vline(xintercept = 0) +
  scale_linetype_manual(name = "Group", labels=c("Control", "Treatment"), values=c( "dashed", "solid"))+
  xlab("Day") + ylab("Performance of president") +
  theme_minimal()
dev.off()

pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/parallel_5.pdf"), width=7,height=4,paper='special')
ggplot(ps, aes(difference, perf_parl, group = treat, linetype=factor(treat))) +
  stat_summary(geom = 'line') +
  geom_vline(xintercept = 0) +
  scale_linetype_manual(name = "Group", labels=c("Control", "Treatment"), values=c( "dashed", "solid"))+
  xlab("Day") + ylab("Performance of parliament") +
  theme_minimal()
dev.off()

pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/parallel_6.pdf"), width=7,height=4,paper='special')
ggplot(ps, aes(difference, perf_local, group = treat, linetype=factor(treat))) +
  stat_summary(geom = 'line') +
  geom_vline(xintercept = 0) +
  scale_linetype_manual(name = "Group", labels=c("Control", "Treatment"), values=c( "dashed", "solid"))+
  xlab("Day") + ylab("Performance of local councilor") +
  theme_minimal()
dev.off()

pdf(file.path(file = "~/Dropbox/Apps/Overleaf/AfricaOutages/parallel_7.pdf"), width=7,height=4,paper='special')
ggplot(ps, aes(difference, democr, group = treat, linetype=factor(treat))) +
  stat_summary(geom = 'line') +
  geom_vline(xintercept = 0) +
  scale_linetype_manual(name = "Group", labels=c("Control", "Treatment"), values=c( "dashed", "solid"))+
  xlab("Day") + ylab("Satisfaction with democracy") +
  theme_minimal()
dev.off()



```






